\begin{biog}

\item[Ronaldo Garcia] is a professor at the Federal University of Goiás, Brazil. He holds a BSc. in electrical engineering and received his doctorate in mathematics from IMPA, Rio de Janeiro, Brazil, under Jorge Sotomayor. His research interests include classical differential geometry, differential equations, and dynamical systems, in particular the qualitative theory of curvature lines and others geometric singular foliations of surfaces and hypersurfaces of Euclidean spaces.
\begin{affil}
Instituto de Matemática e Estatística\\
Universidade Federal de Goiás\\
Goiânia, Brazil, 74690-900\\
{ragarcia@ufg.br}
\end{affil}

\item[Dan Reznik] is director at Data Science Consulting, Rio de Janeiro, Brazil. He holds a Ph.D. in computer science from the University of California, Berkeley, having worked in such fields as automation, robotics, solar Energy, and advanced data analytics.
\begin{affil}
Data Science Consulting\\
Rio de Janeiro, Brazil\\
{dreznik@gmail.com}
\end{affil}

\item[Jair Koiller] was Visiting Professor at the Mathematics Department of the Federal University of Juiz de Fora and retired professor in the Mathematics Institute at Federal University of Rio de Janeiro, Brazil. His research is on applied tools of differential geometry and dynamical Systems. He has collaborated in such areas as astronomy, physics, engineering and biology. His recent interests include applied social sciences and education, especially outreach science projects.

\begin{affil}
Universidade Federal do Rio de Janeiro\\
Rio de Janeiro, Brazil\\
{jairkoiller@gmail.com}
\end{affil}
\end{biog}