Videos mentioned above have been placed on a \href{https://bit.ly/379mk1I}{playlist} \cite{reznik2020-playlist-circum}. Table~\ref{tab:playlist} contains quick-reference links to all videos mentioned, with column ``PL\#'' providing video number within the playlist.

Additionally to Conjecture~\ref{conj:moses} we submit the following questions to the reader:

\begin{itemize}
  \item Can alternate proofs be found for Theorems~\ref{thm:axis-ratio} and \ref{thm:focal-ratio} with tools of algebraic and/or projective geometry?
  \item Are there other notable circumconic pairs which exhibit interesting invariants?
  \item Can any of the invariants cited above be generalized to $N$-periodics?
  \item Can the invariant aspect ratios for the Excentral Inconics mentioned in Section~\ref{sec:inconic} be proven?
    \item Are there other Inconic invariants over 3-periodics and/or their derived triangles? 
    \item Are there interesting properties for the loci of the {\em foci} of Feuerbach and/or Jerabek Circumhyperbolas?
    \item The Yff Circumparabola whose focus is on $X_{190}$ is shown in \cite[PL\#12]{reznik2020-playlist-circum} over 3-periodics. Are there interesting invariants?
    \item Does any Triangle Circumcubic display interesting invariants over 3-periodics? We found none for the Thomson Cubic shown in \cite[PL\#13]{reznik2020-playlist-circum}. How about the Darboux, Neuberg, Lucas, and myriad others catalogued in \cite{gibert2020-cubics}.
    \item The ratio of focal lengths of $F$ by $J_{exc}$ is numerically invariant for the Poristic family. Can this be proved?
    \item Like 3-periodics, poristic triangles conserve $r/R$. Can a continuous map be specified between the two families? Are there any interesting properties?
\end{itemize}

\begin{table}
%\scriptsize
\begin{tabular}{c|l|l}
\href{https://bit.ly/2NOOIOX}{PL\#} & Title & Section\\
\hline

\href{https://youtu.be/tMrBqfRBYik}{01} &
{Mittenpunkt stationary at EB center} & \ref{sec:intro} \\

\href{https://youtu.be/vSCnorIJ2X8}{02} &
{Circumbilliards (CB) of Various Triangles} &
\ref{sec:cb} \\

\href{https://youtu.be/Og7xLgkrLqw}{03} &
{CBs of Derived Triangles and Loci of Centers} &
\ref{sec:cb_derived} \\

\href{https://youtu.be/xyHUwpvAj3g}{04} & CBs of ACT and Medial (separate) &
\ref{sec:cb_derived} \\

\href{https://youtu.be/e-mToZlkHtc}{05} &
CBs of ACT and Medial (superposed) & \ref{sec:cb_derived} \\

\href{https://youtu.be/5KL8st2vIb0}{06} &
{CB of Orthic and Locus of its Mittenpunkt} &
\ref{sec:cb_derived} \\

\href{https://youtu.be/yEu2aPiJwQo}{07} & \makecell[lt]{Invariant Aspect Ratio of \\Circumbilliard of Poristic Family} &
\ref{sec:cb_derived} \\

\href{https://youtu.be/P_Io7HsWGnQ}{08} &
{The $X_1$- and $X_2$-centered Circumellipses} &
\ref{sec:circumellipses} \\

\href{https://youtu.be/Pz4tUijYZCA}{09} &
\makecell[lt]{Orbit Feuerbach and \\ Excentral Jerabek Circumhyperbolas} &
\ref{sec:circumhyperbolae} \\

%\href{https://youtu.be/7Q1TCbW2jFM}{10} &
%Excentral CB and its Jerabek Hyperbola &
%\ref{sec:circumhyperbolae} \\

\href{https://youtu.be/ewioM6-nCpY}{10} &
Invariant Focal Length Ratio for $F$ and $J_{exc}$ &
\ref{sec:circumhyperbolae} \\

\href{https://youtu.be/CHbrZvx1I8w}{11} &
\makecell[lt]{
Excentral MacBeath and $X_3$-Centered\\Inconics: Invariant Aspect Ratio
} &
\ref{sec:inconic} \\

\href{https://youtu.be/Sm9g5lqhZbk}{12} & The Yff Circumparabola of 3-Periodics &
\ref{sec:conclusion} \\

\href{https://youtu.be/s-h72iorZKw}{13} & The Thomson Cubic of 3-Periodics &
\ref{sec:conclusion} \\

%\href{https://youtu.be/DS4ryndDK6Q}{15} & Invariants of the Poristic Triangle Family &
%\ref{sec:conclusion} \\

\end{tabular}
\caption{Videos mentioned in the paper. Column ``PL\#'' indicates the entry within the playlist \cite{reznik2020-playlist-circum}}
\label{tab:playlist}
\end{table}
